Figures

### 2020-02-28 figures/01_contrasts.Rmd
figure resizing

```{r 01_contrasts, echo=FALSE, message=FALSE, eval=TRUE, warning=FALSE, results='hide', fig.height = 4}
theme_opts <- theme(axis.text.x = element_text(angle = 90), 
                    axis.title = element_blank(),
                    plot.title = element_text(size = 8))

>>>>

```{r 01_contrasts, echo=FALSE, message=FALSE, eval=TRUE, warning=FALSE, results='hide', fig.height = 3.5}
theme_opts <- theme(axis.text.x = element_text(angle = 90), 
                    axis.title = element_blank(),
                    plot.title = element_text(size = 8))

### 2020-02-28 manuscript/figures.Rmd
figure resizing

```{r metric_correlations, fig.cap = "Pearson correlation coefficients of map-derived metrics against inlake slope and deepest point distance metrics.", warning=FALSE, echo = FALSE, eval=TRUE, out.extra=''}
knitr::include_graphics("../figures/metric_correlations-1.pdf")
```

\captionsetup[figure]{name=Table}
\captionsetup[figure]{labelformat=empty}
```{r depth_model_metrics, fig.cap = "Table 2: Model fit and predictive accuarcy metrics for all combinations of true and proxy slopes and distances. ", warning=FALSE, echo = FALSE, eval=TRUE, out.extra=''}
knitr::include_graphics("../tables/depth_model_metrics-1.pdf")
```
\captionsetup[figure]{name=Figure}
\captionsetup[figure]{labelformat=default}
\setcounter{figure}{5}

@@

```{r contrasts, fig.cap = "Lake characteristics by categorical variables.", warning=FALSE, echo = FALSE, eval=TRUE}
knitr::include_graphics("../figures/01_contrasts-1.pdf")
```

@@

```{r glaciated_vs_shapeclass, fig.cap = "Cross tabulation between lake glaciation and shape class. Circles are proportional to the number of lakes in each category. If a lake has been glaciated it is more likely to be convex. However, if a lake has not been glaciated there is no tendencey towards a particular shape class.", warning=FALSE, echo = FALSE, eval=TRUE}
knitr::include_graphics("../figures/glaciated_vs_shapeclass-1.pdf")
```

@@

```{r 01_geometry_map, fig.cap = "Green points show the 'visual center' of the lake. Red points show the true deepest point of a lake.", warning=FALSE, echo = FALSE, eval=TRUE}
knitr::include_graphics("../figures/gg_distance-3.pdf")
```

>>>>

```{r metric_correlations, fig.cap = "Pearson correlation coefficients of map-derived metrics against inlake slope and deepest point distance metrics.", warning=FALSE, echo = FALSE, eval=TRUE, out.extra='', out.width="11cm", fig.align='center'}
knitr::include_graphics("../figures/metric_correlations-1.pdf")
```

\captionsetup[figure]{name=Table}
\captionsetup[figure]{labelformat=empty}
```{r depth_model_metrics, fig.cap = "Table 2: Model fit and predictive accuarcy metrics for all combinations of true (inlakeslope, distdeepest) and proxy (slopemean, distviscenter) metrics.", warning=FALSE, echo = FALSE, eval=TRUE, out.extra='', fig.align='center'}
knitr::include_graphics("../tables/depth_model_metrics-1.pdf")
```
\captionsetup[figure]{name=Figure}
\captionsetup[figure]{labelformat=default}
\setcounter{figure}{5}

@@

```{r contrasts, fig.cap = "Lake characteristics by categorical variables.", warning=FALSE, echo = FALSE, eval=TRUE, out.extra=''}
knitr::include_graphics("../figures/01_contrasts-1.pdf")
```

@@

```{r glaciated_vs_shapeclass, fig.cap = "Cross tabulation between lake glaciation and shape class. Circles are proportional to the number of lakes in each category. If a lake has been glaciated it is more likely to be convex. However, if a lake has not been glaciated there is no tendencey towards a particular shape class.", warning=FALSE, echo = FALSE, eval=FALSE}
knitr::include_graphics("../figures/glaciated_vs_shapeclass-1.pdf")
```

@@

```{r 01_geometry_map, fig.cap = "Green points show the 'visual center' of the lake. Red points show the true deepest point of a lake.", warning=FALSE, echo = FALSE, eval=FALSE}
knitr::include_graphics("../figures/gg_distance-3.pdf")
```
